MINOS Handover Plots

### 2023-08-17 minos/validation/handovers.Rmd
Tried a marital status module and tried using longitudinal data for nnet models (and used this for education model and predicting max_educ for repl pops

```{r}
raw.s <- raw.parity %>%
  select(pidp, age, time, nkids_ind)
base.s <- base.parity %>%
  select(pidp, age, time, nkids_ind)

@@

spaghetti_plot(spag, 'nkids_ind',
               save = shall.we.save,
               save.path = save.path)

@@

```{r}

>>>>

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Total nkids

```{r}
prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')

## Marital Status

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'marital_status')

tit <- 'Marital Status'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = marital_status, colour = marital_status)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=marital_status)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'marital_status.png',
         plot = last_plot(),
         path = save.path)
}

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, marital_status)
base.s <- base.dat %>%
  select(pidp, age, time, marital_status)

@@

spaghetti_plot(spag, 'marital_status',
               save = shall.we.save,
               save.path = save.path)

@@

## Education State
